Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} Model System

### 2014-05-29 paper_enahpc14/RebuttalLetter/rebuttal.tex

In 4.3
Only -O3 is not appropriate for the Sandy bridge and Ivy Bridge system. At
least -mavx should be added. It looks like some low hanging fruit is reserved
to reach the targeted 5x improvement

%%% *** Will ***
\begin{weSay}
blabla
\end{weSay}

In 5.1
The blocking mode does not seem to be blocking. As there are no other
processes/threads available (as many MPI ranks as cores per node) the waiting
ranks will repeatedly call sched\_yield() only to be picked again by the OS
scheduler. This also explains the small benefit as no idle states are used.
You should check the CPU utilization. I guess it is 100\% on all cores in both
modes. If it is not, you should check with powertop which idle states are used.

%%% *** Manuel/Sandra ***
\begin{weSay}
We noticed the problem and fixed accordingly along the manuscript the misused blocking term.
Now we refer to ``aggressive'' and ``degraded'' OpenMPI policies instead of ``polling''
and ``blocking''. The reviewer is completely right on this issue, however even with 
the ``degraded'' policy the CPU utilization is readuced to 50\,\%, thus saving energy.
\end{weSay}

### 2014-05-29 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes + rebuttal letter

\begin{figure*}[ht]
  \centering
  \scriptsize
  Simulation of 1 hour during midday (11h--12h) using the \emph{aggressive} MPI policy \\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}} \\
  Simulation of 1 hour during midday (11h--12h) using the \emph{degraded} MPI policy \\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}} \\
  1 hour simulation during midnight (23h--24h) using the \emph{aggressive} MPI policy \\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}} \\
  1 hour simulation during midnight (23h--24h) using the \emph{degraded} MPI policy \\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}} \\
  \begin{tabular}{rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rl}
    & &  & &  & &  \\[-0.15cm]
    Computation     & \multicolumn{1}{>{\columncolor[RGB]{  0,  , 255}}p{0.4cm}}{} & & 
    Block. send     & \multicolumn{1}{>{\columncolor[RGB]{255,  0,174}}p{0.4cm}}{} & & 
    Synchronization & \multicolumn{1}{>{\columncolor[RGB]{179,  0,  0}}p{0.4cm}}{} & & 
    Wait/Wait all   & \multicolumn{1}{>{\columncolor[RGB]{235,255,  0}}p{0.4cm}}{} \\
    & &  & &  & &  \\[-0.15cm]
    Immediate recv. & \multicolumn{1}{>{\columncolor[RGB]{100,100,177}}p{0.4cm}}{} & &
    Waiting a msg.  & \multicolumn{1}{>{\columncolor[RGB]{255,  0  ,0}}p{0.4cm}}{} & & 
    Group comm.     & \multicolumn{1}{>{\columncolor[RGB]{255,144, 26}}p{0.4cm}}{} & &
    Others          & \multicolumn{1}{>{\columncolor[RGB]{192,224,  0}}p{0.4cm}}{} \\
    %I/O             & \multicolumn{1}{>{\columncolor[RGB]{172,174, 41}}p{0.4cm}}{} & &
    %
    %Idle            & \multicolumn{1}{>{\columncolor[RGB]{117,195,255}}p{0.4cm}}{} \\
  \end{tabular}
  \caption{Power-performance   traces  during   midday   and  midnight
    leveraging the \emph{aggressive} and \emph{degraded} MPI policies on \tinto.}
  \label{fig:6}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \scriptsize
  1 hour simulation during midday (11h--12h) using the \emph{aggressive} MPI policy \\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}} \\
  1 hour simulation during midday (11h--12h) using the \emph{degraded} MPI policy \\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}} \\
  1 hour simulation during midnight (23h--24h) using the \emph{aggressive} MPI policy \\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}} \\
  1 hour simulation during midnight (23h--24h) using the \emph{degraded} MPI policy \\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}} \\
  \begin{tabular}{rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rl}
    & &  & &  & &  \\[-0.15cm]
    Computation     & \multicolumn{1}{>{\columncolor[RGB]{  0,  , 255}}p{0.4cm}}{} & & 
    Block. send     & \multicolumn{1}{>{\columncolor[RGB]{255,  0,174}}p{0.4cm}}{} & & 
    Synchronization & \multicolumn{1}{>{\columncolor[RGB]{179,  0,  0}}p{0.4cm}}{} & & 
    Wait/Wait all   & \multicolumn{1}{>{\columncolor[RGB]{235,255,  0}}p{0.4cm}}{} \\
    & &  & &  & &  \\[-0.15cm]
    Immediate recv. & \multicolumn{1}{>{\columncolor[RGB]{100,100,177}}p{0.4cm}}{} & &
    Waiting a msg.  & \multicolumn{1}{>{\columncolor[RGB]{255,  0  ,0}}p{0.4cm}}{} & & 
    Group comm.     & \multicolumn{1}{>{\columncolor[RGB]{255,144, 26}}p{0.4cm}}{} & &
    Others          & \multicolumn{1}{>{\columncolor[RGB]{192,224,  0}}p{0.4cm}}{} \\
    %I/O             & \multicolumn{1}{>{\columncolor[RGB]{172,174, 41}}p{0.4cm}}{} & &
    %
    %Idle            & \multicolumn{1}{>{\columncolor[RGB]{117,195,255}}p{0.4cm}}{} \\
  \end{tabular}
  \caption{Power-performance   traces  during   midday   and  midnight
    leveraging the \emph{aggressive} and \emph{degraded} MPI policies on \tinto.}
  \label{fig:6}
\end{figure*}
